---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# samplrData

<!-- badges: start -->
  [![R-CMD-check](https://github.com/lucas-castillo/samplrData/actions/workflows/R-CMD-check.yaml/badge.svg)](https://github.com/lucas-castillo/samplrData/actions/workflows/R-CMD-check.yaml)
  <!-- badges: end -->

The goal of samplrData is to provide datasets collected by the [SAMPLING project](https://sampling.warwick.ac.uk/). 

## Installation
You can install the development version of samplrData from [GitHub](https://github.com/) with:

``` r
# install.packages("devtools")
devtools::install_github("lucas-castillo/samplrData")
```
## Licenses
Unless otherwise stated, data are distributed under a [CC BY 4.0](https://creativecommons.org/licenses/by/4.0/) license. This means that attribution to the authors of the originating papers is needed. Dataset documentations include who to attribute under the "References" section. 

## Example
Loading the package allows you to import the datasets:

```{r example}
library(samplrData)
knitr::kable(head(sundh2023.meanvariance.e3))
```

Please read descriptions of the datasets in the reference section. 
